That's No Moon: New Analysis Shows No Evidence for Lunar Companion Orbiting Kepler-1625b

### 2019-01-16 ms.tex
data reduction

@@

We reduced the \HST\ data using custom software developed in \cite{kreidberg14a}. We used the \texttt{flt} data product provided by STScI, which is corrected for dark current, bias, and nonlinearity. The \texttt{flt} files are also flatfielded, and cosmic rays are rejected based on a fit to the up-the-ramp samples.  To begin the data reduction, we fit the centroid of the direct image with a two-dimensional Gaussian. The centroid position determines the position of the spectral trace, which we calculated using the coeffients provided in the configuration file from STScI: \texttt{G141.F130N.V4.32.conf}\footnote{available at \url{http://www.stsci.edu/hst/wfc3/analysis/grism_obs/calibrations/wfc3_g141.html}}.  We then created an extraction box centered on the spectral trace. We varied the height and width of the box in 1-pixel increments to find the window that minimized the root-mean-square (rms) deviation from the best fit to the transit light curve. The best was FIXME .

Using this window, we reduced the grism exposures with the optimal extraction routine of \citep{horne86}, which minimizes background noise in the extracted spectrum by weighting pixels that are dominated by the target spectrum more heavily than pixels dominated by the background.  The inputs for the optimal extraction are the background-subtracted data array, the error array (including photon noise read noise, and uncertainty due to background subtraction), an initial guess for the spectrum and its uncertainty, and a mask array for bad pixels.  For the error array, we used a quadrature sum of the photon noise (the square root of the pixel counts), the read noise (12 electrons for \texttt{flt} files, according to the WFC3 data handbook), and the error due to background subtraction (described in \ref{sec:background}).  We initially masked  pixels with the data quality flag 4 or 512 (dead pixels or blobs). For the initial guess of the spectrum and its uncertainty, we did a simple box extraction (sum over all rows in the extraction window), and assumed the variance was equal to the box-extracted spectrum (expected for photon noise limit). See \ref{sec:background} for further detail on background subtraction.

In brief, optimal extraction is an iterative procedure with the following steps. First, we create a smoothed image by median-filtering each row of the data with a 9-pixel-wide window.  We then normalize the smoothed image by dividing each column by its sum, and multiply it by the best guess spectrum. We compare the smoothed image to the real data and mask outliers in the data that are greater than a threshold $\sigma_\mathrm{cut}$. We then recompute the best guess spectrum with the new mask and the optimal weights from \cite{horne86}. The process is iterated until no outliers greater than the threshold remain.  This procedure masks any cosmic rays or bad pixels that were missed by the initial \texttt{flt} calibration.  We tested a range of thresholds ($4 < \sigma_\mathrm{cut} < 15$) and found that different $\sigma_\mathrm{cut}$ choices did not significantly change the final transit light curve. The data reported in this work use $\sigma_\mathrm{cut} = 15$.

@@

\subsection{Pointing Drift Measurement}
The position of the spectrum on the detector shifts slightly over time ($\sim0.1$ pixel/day) due to the spacecraft's pointing drift. This drift can change the flux measured for the target star: if the spectrum moves onto less sensitive pixels, fewer photoelectrons are recorded. To enable a correction for this effect, we measured the position of the spectrum over time.  To measure shifts in the spatial direction, we first summed each \texttt{flt} image over all columns (which we dub the ``column sum"). We used the first exposure in the visit as a template, and for each subsequent exposure, we used least-squares minimization to calculate the shift in pixels that minimized the difference between its column sum and the template. The shifts are a fraction of a pixel, so we used the NumPy \texttt{interp} routine to do linear interpolation on a sub-pixel scale. The WFC3 point spread function is undersampled, so we convolved each column sum with a 4-pixel-wide Gaussian  before the interpolation \citep[following][]{deming13}.

@@

\section{Analysis}
We fit the light curves with the \texttt{planetplanet} package

@@

>>>>

\usepackage{amsmath}
\newcommand{\Mod}[1]{\ \mathrm{mod}\ #1}

@@

We reduced the \HST\ data using custom software developed in \cite{kreidberg14a}.  This software has yielded consistent results with multiple independent pipelines \citep[e.g.][]{knutson14b, spake18}.  We ran our pipeline on the \texttt{flt} data product provided by the Space Telescope Science Institute (STScI). The \texttt{flt} files are corrected for dark current, bias, and nonlinearity, and they are cleaned of cosmic ray hits based on a fit to the up-the-ramp samples. In keeping with previous WFC3 analysis, we discarded the first orbit of data, where the instrument systematics have larger amplitude.

To begin the data reduction, we fit the centroid of the direct image with a two-dimensional Gaussian. The centroid position determines the position of the spectral trace, which we calculated using the coeffients provided in the configuration file from STScI: \texttt{G141.F130N.V4.32.conf}\footnote{available at \url{http://www.stsci.edu/hst/wfc3/analysis/grism_obs/calibrations/wfc3_g141.html}}.  To process the spectra, we flatfielded the raw data using the spectroscopic flatfield coefficients provided by STScI in \texttt{WFC3.IR.G141.flat.2.fits}, following the instructions in Section 6 of the aXe User Manual\footnote{\url{http://axe-info.stsci.edu/}}.  We then created an extraction box centered on the spectral trace. We varied the height and width of the box in 1-pixel increments to find the window that minimized the root-mean-square (rms) deviation from the best fit to the transit light curve. The best was FIXME .

We reduced the grism exposures with the optimal extraction routine of \citep{horne86}, which minimizes background noise in the extracted spectrum by weighting pixels that are dominated by the target spectrum more heavily than pixels dominated by the background.  The inputs for optimal extraction are the background-subtracted data array, the error array (including photon noise read noise, and uncertainty due to background subtraction), an initial guess for the spectrum and its uncertainty, and a mask array for bad pixels.  For the initial guess of the spectrum and its uncertainty, we did a simple box extraction (sum over all rows in the extraction window), and assumed the variance was equal to the box-extracted spectrum (expected for photon noise limit).  We measured and subtracted the background from the data array as described in \ref{sec:background}. For the error array, we used a quadrature sum of the photon noise (the square root of the pixel counts), the read noise (12 photoelectrons for \texttt{flt} files; WFC3 Data Handbook\footnote{\url{http://www.stsci.edu/hst/wfc3/documents/handbooks/currentDHB/}}), and the error due to background subtraction (described in \ref{sec:background}).  The initial bad pixel mask included pixels marked with the data quality flag 4 or 512 (dead pixels or blobs).

In brief, optimal extraction is an iterative procedure with the following steps. First, we created a smoothed image by median-filtering each row of the data with a 9-pixel-wide window.  We then normalized the smoothed image by dividing each column by its sum, and multiplied it by the best guess spectrum. We compared the smoothed image to the real data and masked outliers in the data that are greater than a threshold $\sigma_\mathrm{cut}$. We then recomputed the best guess spectrum with the new mask and the optimal weights from \cite{horne86}. The process is iterated until no outliers greater than the threshold remain.  This procedure masks any cosmic rays or bad pixels that were missed by the initial \texttt{flt} calibration.  We tested a range of thresholds ($4 < \sigma_\mathrm{cut} < 15$) and found that different $\sigma_\mathrm{cut}$ choices did not significantly change the final transit light curve. The data reported in this work use $\sigma_\mathrm{cut} = 15$.

@@

\subsection{Pointing Drift Measurement}
The position of the spectrum on the detector shifts slightly over time ($\sim0.1$ pixel/day) due to the spacecraft's pointing drift. This drift can change the flux measured for the target star: if the spectrum moves onto less sensitive pixels, fewer photoelectrons are recorded. To enable a correction for this effect, we measured the position of the spectrum over time.

To measure shifts in the spatial direction, we first summed each \texttt{flt} image over all columns (which we dub the ``column sum"). We used the first exposure in the visit as a template, and for each subsequent exposure, we used least-squares minimization to calculate the shift in pixels that minimized the difference between its column sum and the template. The shifts are a fraction of a pixel, so we used the NumPy \texttt{interp} routine to do linear interpolation on a sub-pixel scale. The WFC3 point spread function is undersampled, so we convolved each column sum with a 4-pixel-wide Gaussian  before the interpolation \citep[following][]{deming13}.

@@

\section{Analysis}
The raw light transit light curve (shown in Figure~\ref{fig:raw}) contains both astrophysical signal and instrument systematic noise that is common to WFC3 data \citep{zhou17}. We model the astrophysics and the instrument systematics simultaneously.

\subsection{Astrophysics Model}
For the astrophysics, we used the \texttt{planetplanet} package \citep{luger17}, a photodynamical code that calculates light curves for multiple occulting bodies orbiting a star. Within \texttt{planetplanet}, the orbits are computed with the N-body integrator \texttt{REBOUND} \citep{rein??}. In our analysis, we considered two astrophysical scenarios: a no-moon model and a moon model. The free parameters for the no-moon model were: the stellar radius, the planet radius, the time of central transit, the planet inclination, and. We used a quadratic limb darkening law and fixed the coefficients to the prediction for FIXME from FIXME.  We also fixed the orbital period to FIXME \citep{teachey18b}. Eccentricity zero, Jupiter mass. Varying this parameters would allow

@@

\subsection{Instrument Systematics Model}
There are two systematic trends in the data. One is the orbit-long ramp, attributed to charge traps in the detector filling up over the orbit \citep{zhou17}. The other is a visit-long

. To model the ramp, we use the nonparametric model for the orbit-long hook from \cite{teachey18b}, which is

and a decorrelation

For exposure number $i$, we 
\begin{equation}
S_i = c_{i\Mod9}\times(1 + aX_i + bY_i) 
\end{equation}
